%!TEX root = ../main.tex

\begin{changemargin}{0.8cm}{0.8cm}

~\vfill{}

\section*{Abstract}
\vskip 0.5em
\ac{TCG} represent a global market where the indexing and sorting of thousands of individual cards is a significant logistical challenge. As collections grow, manual sorting becomes inefficient, yet commercial automated solutions remain cost-prohibitive and rely on closed-source software ecosystems. Furthermore, traditional text-based identification methods, such as \ac{OCR}, often fail in this domain due to the prevalence of localized artistic fonts, varying languages and environmental visual noise. The primary challenge is the lack of accessible, open-source hardware and software platforms capable of robust visual card identification. Here we present an open-source robotic sorting platform integrated with a deep metric learning computer vision pipeline that identifies \ac{TCG} cards based on holistic visual similarity. By applying an \ac{arcface} to a \acs{ResNet}-50 backbone, the system mapped card artworks into a 512-dimensional Euclidean space, enabling fast vector retrieval. To overcome the absence of labeled real-world datasets, we developed a synthetic data generation pipeline that blended digital card templates onto stochastic backgrounds, simulating physical artifacts like lens glare, sensor noise and partial occlusions. This methodology effectively bridged the domain shift between digital scans and physical objects. Our experimental results demonstrated a 97.8\,\% Top-1 retrieval accuracy on unconstrained physical photographs without training on any real-world images. We anticipate this open-source architecture will serve as a baseline for accessible robotic sorting and enable the automated generation of large-scale, real-world \ac{TCG} datasets in the future.

\vskip 1em

{\bf Keywords} \Keywords

\vskip 2.5cm

\end{changemargin}
