\chapter{List of Software Used}\label{app:C}

\section{Standard Software Tools}
\begin{itemize}
    \item Helix\footnote{\url{https://helix-editor.com/}}: A text editor used for writing the source code and the text of this thesis.
\end{itemize}

\subsection*{Typographical Note}
This document was typeset using the \LaTeX{}\footnote{\url{https://www.latex-project.org/}} document preparation system originally developed by Leslie Lamport and compiled using the Lua\LaTeX{}\footnote{\url{https://www.luatex.org/}} engine. Hyperlinks and cross-references were handled by the \texttt{hyperref} package created by Sebastian Rahtz and Heiko Oberdiek. The diagrams and graphs were drawn using the Ti\ii{k}Z graphics system by Till Tantau.

\section{Tools Using Machine Learning and Language Models}
In accordance with the \ii{Methodological guideline No. 5/2023}\footnote{\url{https://www.cvut.cz/sites/default/files/content/d1dc93cd-5894-4521-b799-c7e715d3c59e/en/20231003-methodological-guideline-no-52023.pdf}}, the following software was used in the development of this thesis:
\begin{itemize}
    \item DeepL Translator\footnote{\url{https://www.deepl.com/en/translator}}: Used for proofreading, grammar verification and refining the English text of this thesis.
    \item NotebookLM\footnote{\url{https://notebooklm.google/}}: Used to assist with literature review and processing relevant research papers.
    \item Google AI Studio\footnote{\url{https://aistudio.google.com/}}: Used for generating pseudocode from the original source code and providing suggestions for the structural improvement of sentences. Version: \ii{Gemini 3.1 Pro Preview}.
\end{itemize}

